---
title: "API Decision"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#"
)
library(sparkts)
```

# Set up the data

```{r connection}
# Connect to spark
sc <- sparklyr::spark_connect(master = "local", version = "2.2.0")
```

```{r data1}
# Dataset 1
std_data <- sparklyr::spark_read_json(
  sc,
  "std_data",
  path = system.file(
    "data_raw/StandardErrorDataIn.json",
    package = "sparkts"
  )
) %>%
  sparklyr::spark_dataframe()
std_data %>% dplyr::collect()
```

```{r data2}
# Dataset 2
melt_data <- spark_read_json(
  sc,
  "melt_data",
  path = system.file(
    "data_raw/Melt.json",
    package = "sparkts"
  )
) %>%
  spark_dataframe()
melt_data %>% dplyr::collect()
```

# Traditional R (S3 / Generics)

Defining the function:

```{r trad}
se_trad <- function(sc, data, x_col, y_col, z_col, new_column_name) {
  # Invoke the function
  invoke_static(
    sc = sc,
    class = "com.ons.sml.businessMethods.methods.StandardError",
    method = "standardError",
    df = data
  ) %>% 
    invoke(
      method = "stdErr1",
      #df = data,
      df = NULL,
      xCol = x_col,
      yCol = y_col,
      zCol = z_col,
      newColName = new_column_name
    )
}
```

Calling the function: 

```{r callTrad}
sdf_se1 <- se_trad(
  sc, std_data, x_col = "xColumn", y_col = "yColumn", z_col = "zColumn",
  new_column_name = "StandardError"
)
sdf_se1 %>% dplyr::collect()
```

# R6

```{r r6}
utils <- R6::R6Class(
  "utils",
  private = list(
    collect = function(data) {
      dplyr::collect(data)
    }
  )
)

se_r6 <- R6::R6Class(
  "se_r6",
  inherit = utils,
  public = list(
    initialize = function(sc, data) {
      init <- invoke_static(
        sc = sc,
        class = "com.ons.sml.businessMethods.methods.StandardError",
        method = "standardError",
        df = data
      )
      private$init <- init
    },
    standard_error = function(
      data = NULL, x_col, y_col, z_col, new_column_name
    ) {
      private$init %>%
        invoke(
          method = "stdErr1",
          df = data,
          xCol = x_col,
          yCol = y_col,
          zCol = z_col,
          newColName = new_column_name
        ) %>%
        private$collect()
    }
  ),
  private = list(
    init = NULL
  )
)
```

Calling the function:

```{r callR6}
# Instantiate the function
p <- se_r6$new(sc = sc, data = std_data)

# Call the standard error method
output <- p$standard_error(
  x_col = "xColumn", y_col = "yColumn", z_col = "zColumn",
  new_column_name = "StandardError"
)

output
```

We can call this a second time with a new dataset without instantiating the class again - just like Scala!

```{r se}
p$standard_error(
  data = melt_data,
  x_col = "one", y_col = "three", z_col = "two", new_column_name = "new_col"
)
```

We can also use chaining

```{r chaining}
se_r6$
  new(sc = sc, data = std_data)$
  standard_error(
    x_col = "xColumn", y_col = "yColumn", z_col = "zColumn",
    new_column_name = "StandardError"
  )
```

# Pros and Cons

Using generics (or S3) and R6 both have their pros and cons. Here is a quick look at them. See [here](https://adv-r.hadley.nz/oo-tradeoffs.html#s3-r6) for more details.

## Generics

Pros:

* Simple
* Widely used
* Built on generic functions
* It's a more traditional way of writing R code
* Supported by Roxygen

Cons:

* Different API to Scala

## R6

Pros:

* Built on encapsulated objects
* Has references semantics (can be modified in place)

Cons:

* May feel unfamiliar to R users
* Not well supported by Roxygen
