---
title: Developing the Package
output: 
  github_document:
    toc: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#"
)
library(sparkts)
library(testthat)
```

# Development Advice

Developing this package further will require a working knowledge of several packages. Detailed below are several links to books, packages and vignettes.

* Tools to make an R developer's life easier: [devtools](https://github.com/r-lib/devtools)
* Keep your code and code documentation together using [Roxygen2](https://github.com/klutometis/roxygen): Check out the vignettes [here](https://cran.r-project.org/web/packages/roxygen2/)
* Test your code with [testthat](https://github.com/r-lib/testthat)

You can read about these tools and the wider R package development world in the [R Packages](http://r-pkgs.had.co.nz) book.

Key functions to know about are:

* devtools::document()
* devtools::test()
* devtools::check()
* devtools::build()

A very good (free) book on general R can be found [here](https://adv-r.hadley.nz).

All of the packages I have mentioned come from the "[tidyverse](https://www.tidyverse.org)" which is a collection of packages that work very well together. A key package which works well with [sparklyr](http://spark.rstudio.com) is called [dplyr](http://dplyr.tidyverse.org). dplyr provides a grammar of data manipulation, providing a consistent set of verbs that solve the most common data manipulation challenges. It is the package to use for data manipulation in R and is R's version of the Python pandas library.

# Generating HTML Documentation

We can generate the HTML from an Rd file using the following code.

```{r build_docs}
tools::Rd2HTML("../../man/scala_list.Rd")
```

This is linked to JIRA ticket [DAPS-433](https://collaborate2.ons.gov.uk/jira/browse/DAPS-433).

# Connecting to Spark
## Cloudera Data Science Workbench [TO BE TESTED]

In order to [connect to Spark on the Cloudera Data Science Workbench](https://blog.cloudera.com/blog/2017/09/how-to-distribute-your-r-code-with-sparklyr-and-cdsw/), the user must configure their connection using the `sparklyr` package. An example of this can be seen below.

```{r sparkCloudera}
library(sparklyr)
 
config <- spark_config()
config[["spark.r.command"]] <- "/opt/cloudera/parcels/CONDAR/lib/conda-R/bin/Rscript"
config$sparklyr.apply.env.R_HOME <- "/opt/cloudera/parcels/CONDAR/lib/conda-R/lib/R"
config$sparklyr.apply.env.RHOME <- "/opt/cloudera/parcels/CONDAR/lib/conda-R"
config$sparklyr.apply.env.R_SHARE_DIR <- "/opt/cloudera/parcels/CONDAR/lib/conda-R/lib/R/share"
config$sparklyr.apply.env.R_INCLUDE_DIR <- "/opt/cloudera/parcels/CONDAR/lib/conda-R/lib/R/include"
 
sc <- spark_connect(master = "yarn-client", config = config)
```

This is linked to JIRA ticket [DAPS-450](https://collaborate2.ons.gov.uk/jira/browse/DAPS-450).

# Testing
## Building Expected Data Outputs
### The Problem

```{r spark, cache = TRUE, include = FALSE}
sc <- sparklyr::spark_connect(master = "local", version = "2.2.0")

# Define the expected data
expected_df <- structure(
  list(
    ref = c(
      "000000000", "111111111", "222222222", 
      "333333333", "444444444", "555555555", "666666666", "777777777"
    ), 
    xColumn = c(
      "200", "300", "400", "500", "600", "700", "800", "900"), 
    yColumn = c(120, 220, 320, 420, 520, 620, 720, 820), 
    zColumn = c(10, 20, 30, 40, 53, 60, 70, 80), 
    stdError = c(
      10.5851224804993, 14.1156934648117, 16.7967753286756, 19.0703353574777, 
      22.351729734926, 22.9194448813965, 24.6125909283282, 26.1943338370632)), 
  .Names = c(
    "ref", "xColumn", "yColumn", "zColumn", "stdError"), 
  row.names = c(NA, -8L), 
  class = c("tbl_df", "tbl", "data.frame")
)

# Read in the data
std_data <- sparklyr::spark_read_json(
  sc,
  "std_data",
  path = system.file(
    "data_raw/StandardErrorDataIn.json",
    package = "sparkts"
  )
) %>%
  sparklyr::spark_dataframe()

# Call the method
output <- sdf_standard_error(
  sc = sc, data = std_data,
  x_col = "xColumn", y_col = "yColumn", z_col = "zColumn",
  new_column_name = "stdError"
) %>%
  dplyr::collect()
```

You may see the following issue when testing:

```{r fail, error = TRUE}
expect_identical(
  output,
  expected_df
)
```

If you use `dput` to generate your expected output, it doesn't store the full numeric data information. To prove this, rounding this information allows the test to pass:

```{r round}
expect_identical(
  output %>% dplyr::mutate(stdError = round(stdError, 2)),
  expected_df %>% dplyr::mutate(stdError = round(stdError, 2))
)
```

### Solution

If you must use `dput`, one way we can keep the full numeric data information is using hexadecimal (binary fractions) data. See `?deparseOpts` for more information.

```{r expectedCorrect}
expected_df <- dput(
  output, control = c("keepNA", "keepInteger", "showAttributes", "hexNumeric")
)
```

Then when we compare the two datasets, we see no errors.

```{r pass}
expect_identical(
  output,
  expected_df
)
```

If you don’t want to use hexadecimal units, for whatever reason, you can get away with using `expect_equal()` instead of `expect_identical()` which adds a tolerance to numerical value comparisons. See `?all.equal` for more information.

You can always just import the data from a JSON file using `sparklyr`, however.

```{r expectJSON, error = TRUE}
expected_df_json <- sparklyr::spark_read_json(
  sc,
  "std_data",
  path = system.file(
    "path/to/jsonfile.json",
    package = "sparkts"
  )
) %>%
  sparklyr::spark_dataframe()
```
