---
title: Building Expected Data Outputs
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#"
)

library(sparkts)
library(testthat)

sc <- sparklyr::spark_connect(master = "local", version = "2.2.0")

# Define the expected data
expected_df <- structure(
  list(
    ref = c(
      "000000000", "111111111", "222222222", 
      "333333333", "444444444", "555555555", "666666666", "777777777"
    ), 
    xColumn = c(
      "200", "300", "400", "500", "600", "700", "800", "900"), 
    yColumn = c(120, 220, 320, 420, 520, 620, 720, 820), 
    zColumn = c(10, 20, 30, 40, 53, 60, 70, 80), 
    stdError = c(
      10.5851224804993, 14.1156934648117, 16.7967753286756, 19.0703353574777, 
      22.351729734926, 22.9194448813965, 24.6125909283282, 26.1943338370632)), 
  .Names = c(
    "ref", "xColumn", "yColumn", "zColumn", "stdError"), 
  row.names = c(NA, -8L), 
  class = c("tbl_df", "tbl", "data.frame")
)

# Read in the data
std_data <- sparklyr::spark_read_json(
  sc,
  "std_data",
  path = system.file(
    "data_raw/StandardErrorDataIn.json",
    package = "sparkts"
  )
) %>%
  sparklyr::spark_dataframe()

# Call the method
output <- sdf_standard_error(
  sc = sc, data = std_data,
  x_col = "xColumn", y_col = "yColumn", z_col = "zColumn",
  new_column_name = "stdError"
) %>%
  dplyr::collect()
```

# The Problem

You may see the following issue when testing:

```{r fail, error = TRUE}
expect_identical(
  output,
  expected_df
)
```

If you use `dput` to generate your expected output, it doesn't store the full numeric data information. To prove this, rounding this information allows the test to pass:

```{r round}
expect_identical(
  output %>% dplyr::mutate(stdError = round(stdError, 2)),
  expected_df %>% dplyr::mutate(stdError = round(stdError, 2))
)
```

# Solution

One way we can keep the full numeric data information is using hexadecimal (binary fractions) data. See `?deparseOpts` for more information.

```{r expectedCorrect}
expected_df <- dput(
  output, control = c("keepNA", "keepInteger", "showAttributes", "hexNumeric")
)
```

Then when we compare the two datasets, we see no errors.

```{r pass}
expect_identical(
  output,
  expected_df
)
```

If you don’t want to use hexadecimal units, for whatever reason, you can get away with using `expect_equal()` instead of `expect_identical()` which adds a tolerance to numerical value comparisons. See `?all.equal` for more information.
